paper3

### 2022-06-30 paper3.Rmd
hyper

```{python}
%time
from hyperopt import fmin, tpe, hp, STATUS_OK, Trials, space_eval
import numpy as np

# configuration spaces/structures using dictionary container type
space = {
  # General Parameters
           'booster': 'gbtree',
     # 'boosting_type': hp.choice('boosting_type', ['gbdt', 'dart']),
     #     'verbosity':
     #       'nthread':

@@

@@

#### 3. Optimization algorithm

```{python}
# Step 3: Optimization algorithm (Tree Parzen Estimator, tpe)
from hyperopt import tpe

tpe_algorithm = tpe.suggest
```

>>>>

```{python}
#%time
from hyperopt import fmin, tpe, hp, STATUS_OK, Trials, space_eval
import numpy as np

# configuration spaces/structures using dictionary container type
param_space = {
  # General Parameters
           'booster': 'gbtree',
     # 'boosting_type': hp.choice('boosting_type', ['gbdt', 'dart']),
     #     'verbosity':
     #       'nthread':

@@

```{python}
import xgboost as xgb

# https://notebooks.githubusercontent.com/view/ipynb?browser=chrome&color_mode=auto&commit=daa2504c337a74778632d44834209425cb6d357f&device=unknown&enc_url=68747470733a2f2f7261772e67697468756275736572636f6e74656e742e636f6d2f4d696c6164536861686964692f46726175642d446574656374696f6e2d5847426f6f73742f646161323530346333333761373437373836333264343438333432303934323563623664333537662f5847426f6f73745f46726175645f446574656374696f6e2e6970796e62&logged_in=false&nwo=MiladShahidi%2FFraud-Detection-XGBoost&path=XGBoost_Fraud_Detection.ipynb&platform=android&repository_id=152300978&repository_type=Repository&version=98
def objective(params, X = X_train, y = y_train, X_early_stop = 100, y_early_stop = 100, n_folds = 10):

    # pos_count = y_train.sum()
    # neg_count = len(y_train) - pos_count
    # imbalance_ratio = neg_count / pos_count

    xgb_clf = xgb.Classifier(**params, n_estimators = 2000, n_jobs = 1)

    xgb_fit_params = {'early_stopping_rounds': 50,
                      'eval_metric': ['logloss'],
                      'eval_set': [(X_early_stop, y_early_stop)],
                      'verbose': True
                      }

    # cv_score = np.mean(cross_val_score(xgb_clf, X_train, y_train, cv = n_folds,
    #                            fit_params = xgb_fit_params, n_jobs = -1,
    #                            scoring = scorer))

    cv_score = np.mean(cohen_kappa_score(xgb_clf,
                                         X_train, 
                                         y_train, 
                                         cv = n_folds, 
                                         fit_params = xgb_fit_params, 
                                         n_jobs = -1, 
                                         scoring = scorer)
                       )

    # hypoeropt minimizes the loss, hence the minus sign behind cv_score
    return {'loss': cv_score, 'status': hyperopt.STATUS_OK, 'params': params}

```{python}
# Classifier:
def hyperparameter_tuning(space):
    model = xgb.XGBClassifier(n_estimators = space['n_estimators'], 
                              max_depth = int(space['max_depth']), 
                              gamma = space['gamma'],
                              reg_alpha = int(space['reg_alpha']),
                              min_child_weight = space['min_child_weight'],
                              colsample_bytree=space['colsample_bytree'])

    evaluation = [( x_train, y_train), ( x_test, y_test)]

    model.fit(x_train, y_train,
            eval_set=evaluation, eval_metric="rmse",
            early_stopping_rounds=10,verbose=False)

    pred = model.predict(x_test)
    accuracy = accuracy_score(y_test, pred>0.5)
    print ("SCORE:", accuracy)
    #change the metric if you like
    return {'loss': -accuracy, 'status': STATUS_OK, 'model': model}

##### Implementing/Choosing the evaluation metric:

#### 3. Optimization algorithm (Tree Parzen Estimator, tpe)

##### Parameter Tuning: Optimizing the Cross Validated Score

We now need to put these together and call Hyperopt's optimization function, fmin, to search for the optimal parameter combination. I will define a new function that implements this optimization and returns the parameters that acheive the highest cross validated score.

The fmin function minimzes the objective function over the paramter space defined by param_space (described below). It takes a Trials object to store the results of all iterations, which can be used later to gain insights about the search process and results. For more about this (and Tree-structured Parzen Estimator, TPE, which Hyperopt uses internally for optimization) see Hyperopt documentation.

```{python}
def tune_xgb(param_space, X_train, y_train, X_early_stop = 100, y_early_stop = 100, n_iter = 100):    
    # scorer = make_scorer(conditional_recall_score, needs_proba=True)

    # hyperopt.fmin will only pass the parameter values to objective. So we need to
    # create a partial function to bind the rest of the arguments we want to pass to objective
    # obj = partial(objective,
    #               # scorer = scorer,
    #               X = X_train,
    #               y = y_train,
    #               X_early_stop = X_early_stop,
    #               y_early_stop = y_early_stop)

    # A trials object that will store the results of all iterations
    trials = Trials()

    fmin(fn = objective, 
         space = param_space, 
         algo = tpe.suggest, 
         max_evals = n_iter, 
         trials = trials)

    # returns the values of parameters from the best trial
    return trials.best_trial['result']['params']

```{python}
tune_xgb(param_space, X_train, y_train, 100, 100, 100)
```

```{python}
trials = Trials()
best = fmin(fn=hyperparameter_tuning,
            space=space,
            algo=tpe.suggest,
            max_evals=100,
            trials=trials)

print (best)

Tuning hyper-parameters of the XGBoost classifier using Bayesian Optimization

if __name__ == "__main__":    
    # Loading the data
    data = pd.read_csv('creditcard.csv')
    X = data.drop('Class', axis = 1)
    y = data['Class']

    # Train/test split, 80/20, random_state set for reproduibility
    X_train, X_test, y_train, y_test = train_test_split(X, y, stratify = y, test_size = 0.2, random_state = 1)

    # Further splitting the initial training set so that 10% of all data(1/8 of 80%) 
    # can be used as the evaluation set by XGBoost for early stopping
    X_train, X_early_stop, y_train, y_early_stop = train_test_split(X_train, y_train, stratify = y_train, test_size = 1/8, random_state = 1)

    # The prior probability distribution of parameters for Bayesian optimization

    param_space = {
  # General Parameters
           'booster': 'gbtree',
     # 'boosting_type': hp.choice('boosting_type', ['gbdt', 'dart']),
     #     'verbosity':
     #       'nthread':

    param_space = {
            'learning_rate': hyperopt.hp.loguniform('learning_rate', np.log(0.01), np.log(0.2)),
            'subsample': hyperopt.hp.uniform('subsample', 0.25, 1),
            'colsample_bytree': hyperopt.hp.uniform('colsample_bytree', 0.7, 1.0),
            'min_child_weight': hyperopt.hp.choice('min_child_weight', [1, 3, 5, 7]),
            'reg_alpha': hyperopt.hp.uniform('reg_alhpa', 0, 1.0),
            # Avoiding lambda = 0. There is a Github issue on strange behaviour with lambda = 0
            'reg_lambda': hyperopt.hp.uniform('reg_lambda', 0.01, 1.0),
            }

      from hyperopt.pyll.stochastic import sample
space = {'subsample': hp.uniform('subsample', 0.25, 1)}
print(sample(space))

      best_params = tune_xgb(param_space, X_train, y_train, X_early_stop, y_early_stop, n_iter = 150)
      print('\tThe best hyper-parameters found:\n')print(*['\t\t%s = %s' % (k, str(round(v, 4))) for k, v in best_params.items()], sep='\n')
```

other references

@@
